Title here

### 2016-08-16 portfolio/text/ms.Rmd
Update references and start listing references in ms

[@kasperski2013]
[@simpson1949]
[@sethi2012b]
[@sethi2014]

@@

[@standevelopmentteam2015]
[@rcoreteam2016]

>>>>

What's been done

[@kasperski2013]
[@sethi2012b]
[@sethi2010b]
[@sethi2014]
[@perruso2005]
[@hilborn2001]
[@edwards2004]
[@trenkel2013]
[@mumford2009]
[@oostenbrugge2002]
[@baldursson1997]
[@jardine2015]
[@sanchirico2008]

Multiple ways one can diversify: 
buy another permit, pick diverse permit, diversify within existing constraints.

@@

[@standevelopmentteam2015]
[@rcoreteam2016]
[@simpson1949]
